% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Guruprerana Shabadi}  & \\
Master's Student in Computer Science & guruprerana.github.io \\
École Polytechnique, France & guruprerana.shabadi@polytechnique.edu \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{École Polytechnique and Université de Paris}{Paris, France}{Parisian Master of Research in Computer Science (MPRI)}{Sep. 2022 - Present}

\item
	\ressubheading{École Polytechnique}{Palaiseau, France}{B.S., Mathematics and Computer Science}{Sep. 2019 - Jun. 2022}
	\begin{itemize}
		\resitem{GPA: \( 4.2/4.0+ \), Summa cum laude}
	\end{itemize}

\end{itemize}

\resheading{Experience}
\begin{itemize}
\item
	\ressubheading{Institute of Informatics, University of Warsaw}{Warsaw, Poland}{Research Intern}{Apr. 2023 - Aug. 2023}
	\begin{itemize}
		\resitem{Advisor: Nathanaël Fijalkow (Automata Theory Group)}
		\resitem{Topic: Programmatic reinforcement learning}
	\end{itemize}
\item
	\ressubheading{INRIA}{Paris, France}{Research Intern}{Jan. 2022 - Mar. 2022}
	\begin{itemize}
		\resitem{Advisor: Caterina Urban (ANTIQUE Team)}
		\resitem{Topic: Static analysis of data science software}
	\end{itemize}
\item
	\ressubheading{Department of Computer Science, École Polytechnique (LIX)}{Palaiseau, France}{Research Intern}{Jun. 2021 - Dec. 2021}
	\begin{itemize}
		\resitem{Advisor: Sergio Mover (Cosynus Team)}
		\resitem{Topic: Accounting for communication delays arising in cyber-physical systems}
	\end{itemize}

\item 
	\ressubheading{Fasfox}{Paris, France}{Software Developer Intern}{Jun. 2020 - Aug. 2020}
	\begin{itemize}
		\resitem{Worked on the development of an application called `Concrete Dispatch' used by large scale construction sites. Involved in all aspects of development including frontend and backend.}
		\resitem{Technologies used: Django, Vue.js, Android}
	\end{itemize}
\end{itemize}

\resheading{Publications}
\begin{itemize}
\item Luca Negrini, \textbf{Guruprerana Shabadi}, Caterina Urban. Static Analysis of Data Transformations in Jupyter Notebooks. In SOAP at PLDI 2023.

\end{itemize}

\resheading{Awards}
	\renewcommand{\arraystretch}{1.2}
	\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\renewcommand{\arraystretch}{1}
		\begin{tabular}[c]{@{}l@{}}Global Undergraduate Awards - Global Winner in Computer Science\\ (recognized for work on \textit{Static Analysis of Data Science Software})\end{tabular} & Sep. 2022\renewcommand{\arraystretch}{1.2}\\
		Labex DigiCosme Scholarship & 2022-2023\\
		Excellence Scholarship from the École Polytechnique Foundation & 2019-2022\\
		DGA Scholarship from the French Directorate General of Armaments & 2021-2022\\
\end{tabular*}
\renewcommand{\arraystretch}{1}

\resheading{Projects}
\begin{itemize}
\item
	\ressubheading{Anemone}{Paris, France}{Entrepreneurial Project}{Oct. 2020 ---}
	\begin{itemize}
		\resitem{As the CTO, I lead the application development team at Anemone}
		\resitem{We are a team of 4 student entrepreneurs building a socio-professional networking platform tailor-made to the needs of the artistic industry}
	\end{itemize}
% \item
% 	\ressubheading{FlapAI}{}{Machine Learning Project, Course: CSE204 at Ecole Polytechnique}{}
% 	\begin{itemize}
% 		\resitem{Implemented neuroevolution and Q-Learning algoritms from scratch to learn how to play the game of Flappy Bird}
% 		%\resitem{Simulated the various blocks using MAX+PlusII simulation tool.}
% 	\end{itemize}

% \item
% 	\ressubheading{Nuit de l'IA Hackathon}{}{Organized by Binet AI and X-UP Start-up Accelerator at Ecole Polytechnique}{Sep. 2019}
% 	\begin{itemize}
% 		\resitem{Member of the winning team at the hackathon}
% 		\resitem{Best implementation of a multilabel classification algorithm for supermarket products}
% 	\end{itemize}

\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
C/C++, Python, Coq, Haskell, JavaScript, Java, HTML-CSS, x86 Assembly
\item[Frameworks:]
Django, Vue.js, Android, React, React Native, Pandas, Scikit-learn, Tensorflow, Qt
\item[Spoken languages:]
English (native), French (advanced working proficiency), Kannada, Hindi
\end{description}

\resheading{Volunteer Experience}
\begin{itemize}
\item
	\ressubheading{Developer Student Club of École Polytechnique}{}{Developer Student Club Lead}{Sep. 2020 - Jun. 2021}
	\begin{itemize}
		\resitem{As a part of the Google DSC Program, led a team in organizing events, workshops, and competitions about various platforms and technologies, including cloud and AI.}
	\end{itemize}

\item 
	\ressubheading{Student Body of École Polytechnique}{}{Chief Financial Officer}{Jun. 2020 - Jun. 2021}
	\begin{itemize}
		\resitem{I was incharge of accounting, and gathering of sponsorships and funds, in addition to organizing the social and cultural life on campus.}
	\end{itemize}
\end{itemize}

\end{document}
